Exploring United States Housing Affordability

### 2016-08-10 paper/Paper.Rmd
fixed the intro and abstract

@@

The dataset was taken from the American Housing Survey, which derives sets of data from 1985 and on. The data set includes categorizing each housing unit by factors such as affordability, income through fair market rent, burden, and the adjusted median income. Certain factors, such as Poverty Income, is based on the Census Bureau's official thresholds.

@@

  The findings in this paper help elucidate income and household burden trends overtime. However, there are many holes in the actual data. The data grabbed uses gross incomes and groups data over large regions of the United States. While the spreads of incomes and housing costs may be low, the internal varation within each region will be fairly high. As a result, this does not help protray a full picture of burden level across the United States, namely in (sub)urban versus non urban areas. Also, the usage of gross income is inaccurate, as the median net income levels varied over time (even after adjusting for inflation), since taxation levels were much higher in the 1950s and 1960s than they are now- which means the burden levels are likely undervalued in the data during those decades.

>>>>

#Introduction

The dataset was taken from the American Housing Survey (AHS), which derives sets of data from 1985 and on. The data set includes categorizing each housing unit by factors such as affordability, income through fair market rent, burden, and the adjusted median income. Certain factors, such as Poverty Income, is based on the Census Bureau's official thresholds.

@@

@@

  The findings in this paper help elucidate income and household burden trends overtime. However, there are many holes in the actual data. The data grabbed uses gross incomes and groups data over large regions of the United States. While the spreads of incomes and housing costs may be low, the internal varation within each region will be fairly high. As a result, this does not help protray a full picture of burden level across the United States, namely in (sub)urban versus non urban areas. Also, the usage of gross income is inaccurate, as the median net income levels varied over time (even after adjusting for inflation), since taxation levels were much higher in the 1950s and 1960s than they are now- which means the burden levels are likely undervalued in the data during those decades. Also, the data provided is given in odd years, which prevents a complete analysis of housing affordability.

    Ultimately, our findings point towards
